### 2024-07-15 analysis/analysis.qmd
updates from our last working together in person

m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = C_summary,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Classification: Summary")

>>>>

m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = studyREF, # unique_id
                 data = C_summary,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Classification: Summary")

### 2024-07-15 analysis/preprocessing.qmd
updates from our last working together in person

g1
```
## Check studies included

```{r}
#| eval: false
included_in_summary <- R_summary$citekey[R_summary$dimension=='arousal']

included_originally <- unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])

included_originally[!included_originally %in% included_in_summary]

@@

R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 50 #resolved
#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved

@@

# Assign
R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
                                                 1000),
                                      labels = c("Feature n < 130","Feature n > 130 & < 653","Feature n > 653"))
table(R_studies$feature_n_complexity)
```

@@

g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey))+
  stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
  geom_point(alpha=0.5,show.legend = F,position = position_jitter(width = .3))+
  #geom_label_repel(size=2,max.overlaps = 50)+
  facet_wrap(dimension~feature_n_complexity)+
  ylab("Correlation Coefficient")+
  xlab("Model Technique")+
#  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
  geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
             stat = "summary", fun = mean,show.legend = F)+
  theme_bw()
g
#ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
```

@@

```{r}
tmp <- metaMER_results
tmp2 <- tmp[which(tmp$statistic=='n'),]
no_of_classes <- summarise(group_by(tmp2,citekey),first(values))
print(no_of_classes)
rm(tmp,tmp2)
```

@@

# Deal with four studies involving multiple datasets: 
C_studies$stimulus_n[C_studies$stimulus_n==" 429; 350 popular songs + 79 songs from the Beatles (Mirex 2009 collection)  "] <- 429 # resolved from the paper
C_studies$stimulus_n[C_studies$stimulus_n==" 5192; 12 per user in user validation (not included here due to little information),   AcousticBrainz validation: 60000  "] <- 5192 # resolved
C_studies$stimulus_n[C_studies$stimulus_n==" ISMIR2012: 2886, NJU_V1: 777, Hindi: 1037  "] <- 2886+777+1037 # decided to take this from validation
C_studies$stimulus_n[C_studies$stimulus_n==" total: 564; unambiguous: 416, circular validation: 39 "] <- 564 # 
C_studies$stimulus_n <- as.numeric(C_studies$stimulus_n)

@@

print(quantile(C_studies$feature_n,c(0.333,0.666),na.rm = TRUE))
#quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)

# Assign
C_studies$feature_n_complexity <- cut(C_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(C_studies$feature_n,c(0.333),na.rm = TRUE)),
                                                 as.numeric(quantile(C_studies$feature_n,c(0.666),na.rm = TRUE)),
                                                 1000),
                                      labels = c("Feature n < 119","Feature n > 119 & < 548","Feature n > 548"))
table(C_studies$feature_n_complexity)
```

@@

g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey))+
  stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
  geom_point(alpha=0.5,show.legend = F,position = position_jitter(width = .3))+
  #geom_label_repel(size=2,max.overlaps = 50)+
  facet_wrap(.~feature_n_complexity)+
  ylab("Correlation Coefficient")+
  xlab("Model Technique")+
  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
  geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
             stat = "summary", fun = mean,show.legend = F)+
  theme_bw()
print(g)
#ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
```

>>>>

g1
```
## Select a summary measure for valence and arousal separately

@@

R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 499 #resolved

R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting = 21')] <- 21
R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'548; after reduct')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and filter bank')] <- 3600
R_studies$feature_n[str_detect(R_studies$feature_n,'Features deep-learned from audio (not specified) but 1802 in DEAM')] <- 260

R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments

@@

# Assign
R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
                                                 10000),
                                      labels = c("Feature n < 236","Feature n > 236 & < 653","Feature n > 653"))

R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,30,300,10000),
                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))

table(R_studies$feature_n_complexity)
```

@@

g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey,shape=stimulus_genre_mixed))+
  stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
  geom_point(alpha=0.5,show.legend = F,position = position_jitter(width = .3))+
  #geom_label_repel(size=2,max.overlaps = 50)+
  facet_wrap(dimension~feature_n_complexity)+
  ylab("Correlation Coefficient")+
  xlab("Model Technique")+
  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
  geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
             stat = "summary", fun = mean,show.legend = F)+
  theme_bw()
g
#ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
```

@@

```{r}
tmp <- metaMER_results
tmp2 <- tmp[which(tmp$statistic=='n'),]
no_of_classes <- summarise(group_by(tmp2,citekey),first(values))
print(no_of_classes)
hist(no_of_classes$`first(values)`)

rm(tmp,tmp2)
```

@@

# Deal with four studies involving multiple datasets: 
C_studies$stimulus_n[C_studies$stimulus_n==" 429; 350 popular songs + 79 songs from the Beatles (Mirex 2009 collection)  "] <- 429 # resolved from the paper
C_studies$stimulus_n[C_studies$stimulus_n==" 5192; 12 per user in user validation (not included here due to little information),   AcousticBrainz validation: 60000  "] <- 5192 # resolved
C_studies$stimulus_n[C_studies$stimulus_n==" ISMIR2012: 2886, NJU_V1: 777, Hindi: 1037  "] <- 2886+777+1037 # decided to take this from validation
C_studies$stimulus_n[C_studies$stimulus_n==" total: 564; unambiguous: 416, circular validation: 39 "] <- 564 # 
#table(C_studies$stimulus_n)
C_studies$stimulus_n <- as.numeric(C_studies$stimulus_n)

@@

ggplot(C_studies,aes(x=feature_n))+geom_histogram()

#print(quantile(C_studies$feature_n,c(0.333,0.666),na.rm = TRUE))
#quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)

# Assign
C_studies$feature_n_complexity <- cut(C_studies$feature_n,
                                      breaks = c(0,30,300,
                                                 10000),
                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))
table(C_studies$feature_n_complexity)
```

@@

g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey,shape=stimulus_genre_mixed))+
  stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
  geom_point(alpha=0.5,show.legend = F,position = position_jitter(width = .3))+
  #geom_label_repel(size=2,max.overlaps = 50)+
  facet_wrap(.~feature_n_complexity)+
  ylab("Correlation Coefficient")+
  xlab("Model Technique")+
  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
  geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
             stat = "summary", fun = mean,show.legend = F)+
  theme_bw()
print(g)
#ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
```

### 2024-07-15 manuscript/manuscript.qmd
updates from our last working together in person

We preregistered our meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).

@@

First we could describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).

@@

@@

| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$| Prediction interval
|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
| Valence All | 49,42480  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% | -0.0719; 0.9260
| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% | 0.4470; 0.7396
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| Arousal     | 55,43160   | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
| Arousal Trim| 27,18402   | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
| Arousal M   | 14,10641   | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
| Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047

@@

>>>>

We preregistered the meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).

@@

First we describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).

@@

|            | Regression                   | Classification |
|:-----------|:-----------------------------|:---------------|
| Study N    | 24                           | 14             |
| Model N    | 258                          | 108            |
| Techniques | Flexible Discriminants: 64   | 37 |
| Techniques | KS, Add. & KNN: 24           | 8 |
| Techniques | Linear Methods: 74           | 24 |
| Techniques | Neural Nets: 74              | 27 |
| Techniques | Random Forests: 22           | 12 |
| Feature N  | Min=3, Md=472.5, Max=654     | Min=3, Md=231, Max=8904 |
| Stimulus N | Min=40, Md=324, Max=2486     |Min=124, Md=387, Max=5192 |

@@

| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$| Prediction interval
|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
| Valence All |           | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim|           | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
| Valence M   |           | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  |           | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 24,15660  | 0.6585 [0.5574; 0.7404] | 7.44|.0001 | 0.142| 97.9% |
| Val. MaxTrim|   13,7363 | 0.6489 [0.5980; 0.6945] | 18.5|.0001 | 0.008| 88.5% |
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| Arousal     |            | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
| Arousal Trim|            | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
| Arousal M   |            | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
| Arousal Md  |            | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
| Arousal Max | 24,15660   | 0.8070 [0.7453; 0.8550] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
| Aro.Max.Trm | 14,12061   | 0.8182 [0.8021; 0.8331] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047

@@

| Model       | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| All         | 89,87347   | 0.8074 [0.7681; 0.8407] |21.4 |0.0001|0.2415|99.7%  |
| All Trim    | 29,6499    | 0.8185 [0.8046; 0.8314] | 58.3|0.0001|0.0066| 60.4%  |
| Max         | 14,17184   | 0.8564 [0.7386; 0.9234] | 8.32|0.0001|0.329 | 99.8% |
| Max Trim    | 6,3653     | 0.8689 [0.7760; 0.9249] | 11.6|0.0001|0.0749| 97.5% |
